Rewind: Automatically Generated\\Digital Memories from Mobile Geolocation Data

### 2016-09-12 paper/uist_2016/paper.tex
Rewrite user study section

\section{User Study}
\subsection{Research Questions}
Rewind enables us to ask questions that have not been possible to ask before, due to the scarcity of comprehensive data about where someone has been. We performed a within-subjects comparison of Rewind and static photography that are not sequenced together. By showing a user both types of digital memories, we can begin to understand what are the features that make the Rewinds more realistic are more believable for different trips.

There are some specific research questions we investigate about people's behaviors surrounding digital memories.

1) Do certain features of a Rewind make it more memorable? Are the participants able to recall a particular location or route most often in Rewinds with particular features?

2) Which Rewinds do users wish to save, and which ones would you like to share? For example, frequent trips close to home, long one-time journeys, or just the destinations and landmarks that the travel takes them to? Are these the Rewinds that are the most familiar, or ones that are unique and are not instantly recognizable?

3) Do people who frequently use a GPS have different memories than those who don't? What about frequent travelers or people who are traveling with companions? Again, this is something that has previously been difficult to study without location histories.

\subsection{Procedure}
A user study following a two-week tracking period with 21 participants from the [anonymized] area investigated the influence of Rewinds on recollection, and evaluated their memorability and believability.

Participants for the study were recruited online through Craigslist classifieds and local Reddit communities for the [anonymized] area. Offline, ads were posted in cafes and other small businesses in the the city. Of the 21 total participants, 13 identified as men and 8 identified as women. Participants ranged from ages under 20 to over 50. Most participants were local residents, with occupations varying from librarian to medical researcher to office worker to musician. A fifth of the participants were undergraduate or graduate students.

Study participation included a location-tracking setup session, at least twelve days of tracking, and a follow-up user study. At the location-tracking setup, participants were asked to activate geolocation tracking on their mobile phones. Participants with Android devices used Google's built-in location reporting services for tracking. iPhone users downloaded Google+ to use the same service. Participants with devices incompatible with Google's location reporting services were provided with an older Android device that used the app GPSLogger\footnote{\url{https://play.google.com/store/apps/details?id=com.mendhak.gpslogger&hl=en}} for tracking. Participants were asked to keep their phone charged and on their person as much as possible for approximately two weeks, until they could come in for a final interview with the experimenters.

At the in-person interview, participants were shown a series of images and accompanying Rewinds that represented the trips they took during the tracking period. The user's GPS data was trimmed so that images and Rewinds are created from only the past fourteen days at most. Of the ten image-Rewind pairs that were shown, five were of trips taken infrequently, three were of trips taken most frequently, and the remaining two were random.

At the beginning of the study, participants were asked for their gender, whether they considered themselves a frequent traveler, and whether they tended to use GPS in places they were already familiar with. Participants who used GPS in familiar locations were considered regular GPS users, and participants who didn't were considered non-regular GPS users.

For each image-Rewind pair, the participant was first shown an image of a location from their GPS data and asked to answer questions about it. Then they were shown a Rewind of the trip during which the image showed up, and the participant was asked to answer questions about the Rewind. While the Rewind was playing, participants could hover over the Rewind panel and scrub backwards and forwards horizontally through the images that composed the video. This allowed participants to ``walk through'' their memory at their own pace.

For both the image and the Rewind, the participants were asked questions related to memory recall. They were first asked whether they remember the locations. If they could, they were then asked to discuss specifics of the location: Participants were asked whether they could name the streets and whether they could name buildings, landmarks, or places around the locations. If the participant was looking at a Rewind, they were also asked whether they remembered the exact trip. To evaluate memorability of the photo or Rewind, participants were asked whether they would keep the image or video, and why or why not. Then they were asked whether they traveled alone or with a companion. Lastly, participants were asked questions related to the believability of the digital memory: was the photo or video accurate to their memory? Why or why not?

In addition to asking questions, we observed the users as they examined the Rewinds of their trips, since they could passively watch the Rewind or actively scrub through the individual images that made up the video. The user study took between 30 minutes to an hour for each participant, and participants were compensated \$30 for their time at the end of the study.

Data from three participants was not included in the results of this study. Two of the aforementioned participants were not able to do the user study. One of those participant's data points consisted of only one location. The participant used a mobile device provided by the study, so it's likely that they did not carry the device on their person. The other participant did not complete the user study due to health and scheduling reasons. The last participant only collected three days of data because they had their phone replaced during the tracking period and did not reactivate Google's location reporting services on the new device. This participant completed the user study, but we did not include the data gathered during this participant's session in the results.

\section{Findings}
The findings of our user study center on the participants' relationship to the Rewinds created from their location data. We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds. We also discuss how the participants interacted with and reacted to their Rewinds. The results use data from user studies conducted with 12 men and 6 women. 6 of 12 participants identified themselves as frequent travelers. Additionally, 6 of 12 participants were regular GPS users.

>>>>

\section{User Study}
\subsection{Research Questions}
The Rewind system enables us to ask questions about people's attitudes and behaviors surrounding digital memories that were not possible to answer before due to the scarcity of comprehensive data about where someone has been. To start to understand what makes a digital memory meaningful to a person, we performed a within-subjects comparison of Rewinds and static photography. By comparing Rewinds to today's most prevalent form of digital memory media, we can begin to distill what features make a Rewind meaningful and representative as a memory of a trip.

Our research questions examine the effectiveness of Rewinds through three aspects: memorability, believability, and desirability.

1) Memorability: Do certain features of a location or trip depicted in a digital memory make the memory more recallable?

2) Believability:  Is the digital memory accurate to the participant's memory? What features make a digital memory accurate or inaccurate?

3) Desirability: Which digital memories do users wish to save? Do certain features make a digital memory more likely to be kept?

\subsection{Participants}
Participants for the user study were recruited online through local Craigslist classifieds and Reddit communities for the Providence area. Offline, ads were posted in cafes and other small businesses in the the city. Of the 21 total participants, 13 identified as men and 8 identified as women. Participants ranged from ages 20 to 50. Most participants were local residents, with occupations including librarian, medical researcher, office worker, IT consultant, musician, and comedian. A fifth of the participants were undergraduate or graduate students.

\subsection{Procedure}
Participants underwent a two-week tracking period followed by a user study which investigated the memorability, believability, and desirability of the Rewinds produced from the two weeks of location data.

Study participation included a setup session for location tracking, at least twelve days of tracking, and a follow-up user study. At the location tracking setup, participants were asked to activate geolocation tracking on their mobile phones. Participants with Android devices used Google's built-in location reporting services for tracking. iPhone users downloaded the Google+ app to use the same service. Participants with devices incompatible with Google's location reporting services were provided with an older Android device that used the GPSLogger\footnote{\url{https://play.google.com/store/apps/details?id=com.mendhak.gpslogger&hl=en}} app for tracking. Participants were asked to keep their phone charged and on their person as much as possible for approximately two weeks, until they could come in for a final interview with the experimenters.

At the in-person interview, participants were shown a series of photos and accompanying Rewinds that represented the trips they took during the tracking period. The participant's geolocation data was trimmed to ensure that photos and Rewind videos were generated from data gathered no earlier than the past two weeks. Participants were shown ten photo-Rewind pairs.  Of the ten pairs, five showed trips taken infrequently, three showed trips taken most frequently, and the remaining two were random.

At the beginning of the study, participants were asked to identify their gender, whether they considered themselves a frequent traveler, and whether they tended to use GPS in places they were already familiar with. Participants who used GPS in familiar locations were considered regular GPS users, and participants who did not were considered non-regular GPS users.

For each photo-Rewind pair, the participant was first shown a photo of one of the locations found in their GPS data. The participant was asked to answer the following questions about the photo:

Do you remember this location? If so, can you name the street? Can you name what is around the location, such as buildings, landmarks, or other places?

Would you want to keep this photo? Why or why not? Were you traveling alone?

If you remember the location, is the photo accurate to your memory? Why or why not? What was different?

The participant was then shown a Rewind of the trip that they were on when the previous location was encountered. While the Rewind was playing, the participant could hover over the Rewind panel and scrub backwards and forwards horizontally through the images that composed the video. This allowed participants to ``walk through'' their memory at their own pace. The participant was asked the following questions while the Rewind played:

Do you remember these locations? Do you remember this trip? Can  you name some of the streets? Can you name what is around these locations, such as buildings, landmarks, or other places?

Would you want to keep this video? Why or why not? Were you traveling alone?

If you remember these locations, is the video accurate to your memory? Why or why not? What was different?

Questions about the photos and Rewinds tested their memorability, believability, and desirability as memory media.

In addition to asking questions, we observed the users as they examined their generated Rewinds, since they could passively watch the Rewind or actively scrub through the individual images that made up the Rewind.

The user study took between 30 minutes to an hour for each participant, and participants were compensated \$30 cash for their time at the end of the study.

Data from three participants was not included in the results of this study. One of the participants' data points consisted of only one location. The participant used a mobile device provided by the study, so it is likely that they did not carry the device on their person. Another participant did not complete the in-person interview portion of the user study due to health and scheduling reasons. The last participant only collected three days of data because they had their phone replaced during the tracking period, and did not reactivate Google's location reporting services on their new device. This participant completed the in-person interview portion of the user study, but we did not include the data gathered during this participant's session in the results.

\section{Findings}
The findings of our user study center on the participants' relationship to the Rewinds generated from their location data. We focus on the participants' judgments of their Rewinds' memorability, believability, and desirability in comparison to their judgments of the photos paired with the Rewinds. We also discuss the participants' interactions with and reactions to their Rewinds. The results use data from the user studies conducted with 12 men and 6 women. Half of the participants identified themselves as frequent travelers. Additionally, half of the participants were regular GPS users, or people who used GPS even in locations already familiar to them.
